---
title: "Call Analysis"
author: "Jeffrey Waring"
date: "April 14, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Who calls me more: Jen or Kris?

Time to answer this important question: does my wife call me more or Kris?
To answer, I logged all incoming calls for 18 months, using [this recipe from IFTTT](https://ifttt.com/applets/161618p-automatically-log-every-call-you-make-on-your-android-phone-to-a-google-spreadsheet).

First, I downloaded the .csv file, and added a header and slightly modified the date stamp column.  Two subsets are created: one for Kris' calls, and one for Jenny's.  Both subsets have a date object column created by concatenating monthh,day, and year factors previously read in.

```{r echo = TRUE}

setwd("C:/Users/Jeffrey.Waring/R projects/Call logging")
df <- read.csv("Calls.csv",header=TRUE)

kris <- df[df$Caller=="Kris Larsen",]

#Now create a date column
kris$Date<-as.Date(paste(as.character(kris$Month),as.character(kris$Day),' ',as.character(kris$Year)),format="%B %d,%Y")
#and a weekday column
kris$Weekday<-c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", 
  "Friday", "Saturday")[as.POSIXlt(kris$Date)$wday + 1]

jenny <- df[df$Caller=="Jenny",]
#Now create a date column
jenny$Date<-as.Date(paste(as.character(jenny$Month),as.character(jenny$Day),' ',as.character(jenny$Year)),format="%B %d,%Y")
#and a weekday column
jenny$Weekday<-c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", 
                "Friday", "Saturday")[as.POSIXlt(jenny$Date)$wday + 1]

```


```{r echo = FALSE}
tot<-nrow(df)
```
In total, I recieved: `r tot` calls from the dates:
```{r echo = FALSE}
range(kris$Date)
```

```{r echo = F}
unknown<-nrow(df[df$Caller=="",])
```
Of these `r unknown` calls,
```{r echo=F}
options(scipen=1, digits=1)
```
`r unknown/tot*100`% were from unknown numbers
```{r echo=F}
df2<-df[!df$Caller=="",]
```
These unknown numbers are excluded from further analysis.

## Now, some analysis

Clearly Kris is the winner for total calls:

```{r echo=TRUE,fig.align='center'}
par(mar = c(2, 8, 4, 2) + 0.1, mgp = c(4, 1, 0), las = 2)
barplot(table(df2$Caller),horiz=TRUE,col="blue",main="Calls by Person",xlab="# of calls",las=1)

box()
```

With a given average calltime of `r mean(kris$length)` seconds, Kris' calls are also longer than average (`r mean(df2$length)` seconds) and Jens' (`r mean(jenny$length)` seconds):




```{r echo = T,fig.align='center'}

hist(kris$length,col="green",breaks = 20,main="Call Durations",xlab="[sec]")
hist(jenny$length,col="purple",add=TRUE,breaks=5)
abline(v=mean(kris$length),col="chartreuse4",lwd=5)
abline(v=mean(jenny$length),col="darkorchid4",lwd=5)
legend('topright', c("Kris","Jenny"),lty=1, lwd=4,bty='n', cex=.75,col=c("green","purple"))
box()
```

Finally, and perhaps least surprisingly, Kris' calls tend to skew to the weekends: when plans need to be made.  Jens' calls tend to be more evenly distributed, with the exception of Wednesday.

```{r echo=T,fig.align='center'}
par(mar = c(2, 8, 4, 2) + 0.1, mgp = c(4, 1, 0), las = 2)
barplot(table(kris$Weekday),las=1,hori=TRUE,col="green")
barplot(table(jenny$Weekday),las=1,hori=TRUE,col="purple",add=TRUE,xlab="# of calls")
legend('topright', c("Kris","Jenny"),lty=1, lwd=4,bty='n', cex=.75,col=c("green","purple"))
box()
```
